---
title: "Floodlight practice effects"
author: "Tim Woelfle"
date: "07.05.2021"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
---

# Main analysis

Performance as a function of number of repetitions
Minimum number of repetitions: 5, minimum number of weeks: 5

## Cognition (SDMT)

```{r}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  predictor = "repetition",
  xlab = "Repetitions",
  bounded.growth.confidence.interval = T,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Finger Pinching)

```{r}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  predictor = "repetition",
  xlab = "Repetitions",
  bounded.growth.confidence.interval = T,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Two Minute Walk)

```{r}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  predictor = "repetition",
  xlab = "Repetitions",
  bounded.growth.confidence.interval = F,
  censor_after = 9, # allow comparison with cognition
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```


# Sensitivity analysis 1

Performance as a function of number of repetitions
Minimum number of repetitions: 10, minimum number of weeks: 10

## Cognition

```{r}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  predictor = "repetition",
  xlab = "Repetitions",
  bounded.growth.confidence.interval = F,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity

```{r}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  predictor = "repetition",
  xlab = "Repetitions",
  bounded.growth.confidence.interval = F,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility

```{r}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  predictor = "repetition",
  xlab = "Repetitions",
  bounded.growth.confidence.interval = F,
  censor_after = 10, # allow comparison with cognition
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

# Sensivity Analysis 2

Performance as a function of weeks since first test
Minimum number of repetitions: 5, minimum number of weeks: 5

## Cognition

```{r}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  predictor = "weeksSinceFirst",
  xlab = "Weeks",
  bounded.growth.confidence.interval = F,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity

```{r}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  predictor = "weeksSinceFirst",
  xlab = "Weeks",
  bounded.growth.confidence.interval = F,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility

```{r}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  predictor = "weeksSinceFirst",
  xlab = "Weeks",
  bounded.growth.confidence.interval = F,
  censor_after = 11, # allow comparison with cognition
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```


# Sensitivity analysis 3

Performance as a function of weeks since first test
Minimum number of repetitions: 10, minimum number of weeks: 10

## Cognition

```{r}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  predictor = "weeksSinceFirst",
  xlab = "Weeks",
  bounded.growth.confidence.interval = F,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity

```{r}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  predictor = "weeksSinceFirst",
  xlab = "Weeks",
  bounded.growth.confidence.interval = F,
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility

```{r}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  predictor = "weeksSinceFirst",
  xlab = "Weeks",
  bounded.growth.confidence.interval = F,
  censor_after = 11, # allow comparison with cognition
  up_to_date = "2021-05-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

