---
title: "Floodlight practice effects"
author: "Tim Woelfle"
date: "04.08.2021"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

# Main analysis

Performance as a function of number of repetitions
Minimum number of repetitions: 5, minimum number of weeks between first and last: 5

## Cognition (e-SDMT)

Floodlight Open test code: "ips" (information processing speed)

```{r main ips}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "e-SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Cognition (e-SDMT corrected)

e-SDMT corrected for dexterity by taking the quotient of correct responses of e-SDMT / Digit Tapping (or in Floodlight's terms: ips / ips_baseline)

```{r main ips_over_ips_baseline}
params = list(
  test_code = "ips_over_ips_baseline",
  test_metric_code = "correct_responses",
  unit = "e-SDMT corrected: Correct Responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Digit Tapping)

Floodlight Open test code: "ips_baseline" (information processing speed baseline)

```{r main ips_baseline}
params = list(
  test_code = "ips_baseline",
  test_metric_code = "correct_responses",
  unit = "Digit Tapping: Correct responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Finger Pinching)

Floodlight Open test code: "pinching"

```{r main pinching}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Draw A Shape)

Floodlight Open test code: "draw_a_shape"

```{r main draw_a_shape}
params = list(
  test_code = "draw_a_shape",
  test_metric_code = "number_shapes_drawn_correctly",
  unit = "Drawing: Shapes Drawn Correctly",
  unit_n = "hand",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Two Minute Walk)

Floodlight Open test code: "two_min_walk"

```{r main two_min_walk}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Speed)

Floodlight Open test code: "five_u_turn"

```{r main five_u_turn speed}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turn_speed_avg",
  unit = "U-Turn: Turn Speed Average",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Turns)

Floodlight Open test code: "five_u_turn"

```{r main five_u_turn turns}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turns",
  unit = "U-Turn: Number of Turns",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Static Balance)

Floodlight Open test code: "static_balance"

```{r main static_balance}
params = list(
  test_code = "static_balance",
  test_metric_code = "sway_path",
  unit = "Static Balance: Sway Path",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Passive Monitoring)

Floodlight Open test code: "mobility"

```{r main mobility}
params = list(
  test_code = "mobility",
  test_metric_code = "life_space_daily",
  unit = "Passive Monitoring: Life Space Daily",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mood (Daily question)

Floodlight Open test code: "daily_questions"

```{r main daily_questions}
params = list(
  test_code = "daily_questions",
  test_metric_code = "mood_response",
  unit = "Daily Question: Mood",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

# Sensitivity analysis 1

Performance as a function of weeks since first test
Minimum number of repetitions: 5, minimum number of weeks between first and last: 5

## Cognition (e-SDMT)

Floodlight Open test code: "ips" (information processing speed)

```{r sens1 ips}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "e-SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Cognition (e-SDMT corrected)

e-SDMT corrected for dexterity by taking the quotient of correct responses of e-SDMT / Digit Tapping (or in Floodlight's terms: ips / ips_baseline)

```{r sens1 ips_over_ips_baseline}
params = list(
  test_code = "ips_over_ips_baseline",
  test_metric_code = "correct_responses",
  unit = "e-SDMT corrected: Correct Responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Digit Tapping)

Floodlight Open test code: "ips_baseline" (information processing speed baseline)

```{r sens1 ips_baseline}
params = list(
  test_code = "ips_baseline",
  test_metric_code = "correct_responses",
  unit = "Digit Tapping: Correct responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Finger Pinching)

Floodlight Open test code: "pinching"

```{r sens1 pinching}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Draw A Shape)

Floodlight Open test code: "draw_a_shape"

```{r sens1 draw_a_shape}
params = list(
  test_code = "draw_a_shape",
  test_metric_code = "number_shapes_drawn_correctly",
  unit = "Drawing: Shapes Drawn Correctly",
  unit_n = "hand",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Two Minute Walk)

Floodlight Open test code: "two_min_walk"

```{r sens1 two_min_walk}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Speed)

Floodlight Open test code: "five_u_turn"

```{r sens1 five_u_turn speed}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turn_speed_avg",
  unit = "U-Turn: Turn Speed Average",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Turns)

Floodlight Open test code: "five_u_turn"

```{r sens1 five_u_turn turns}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turns",
  unit = "U-Turn: Number of Turns",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Static Balance)

Floodlight Open test code: "static_balance"

```{r sens1 static_balance}
params = list(
  test_code = "static_balance",
  test_metric_code = "sway_path",
  unit = "Static Balance: Sway Path",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Passive Monitoring)

Floodlight Open test code: "mobility"

```{r sens1 mobility}
params = list(
  test_code = "mobility",
  test_metric_code = "life_space_daily",
  unit = "Passive Monitoring: Life Space Daily",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mood (Daily question)

Floodlight Open test code: "daily_questions"

```{r sens1 daily_questions}
params = list(
  test_code = "daily_questions",
  test_metric_code = "mood_response",
  unit = "Daily Question: Mood",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 5,
  min_weeks = 5,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

# Sensitivity analysis 2

Performance as a function of number of repetitions
Minimum number of repetitions: 10, minimum number of weeks between first and last: 10

## Cognition (e-SDMT)

Floodlight Open test code: "ips" (information processing speed)

```{r sens2 ips}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "e-SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Cognition (e-SDMT corrected)

e-SDMT corrected for dexterity by taking the quotient of correct responses of e-SDMT / Digit Tapping (or in Floodlight's terms: ips / ips_baseline)

```{r sens2 ips_over_ips_baseline}
params = list(
  test_code = "ips_over_ips_baseline",
  test_metric_code = "correct_responses",
  unit = "e-SDMT corrected: Correct Responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Digit Tapping)

Floodlight Open test code: "ips_baseline" (information processing speed baseline)

```{r sens2 ips_baseline}
params = list(
  test_code = "ips_baseline",
  test_metric_code = "correct_responses",
  unit = "Digit Tapping: Correct responses",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Finger Pinching)

Floodlight Open test code: "pinching"

```{r sens2 pinching}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Draw A Shape)

Floodlight Open test code: "draw_a_shape"

```{r sens2 draw_a_shape}
params = list(
  test_code = "draw_a_shape",
  test_metric_code = "number_shapes_drawn_correctly",
  unit = "Drawing: Shapes Drawn Correctly",
  unit_n = "hand",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Two Minute Walk)

Floodlight Open test code: "two_min_walk"

```{r sens2 two_min_walk}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Speed)

Floodlight Open test code: "five_u_turn"

```{r sens2 five_u_turn speed}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turn_speed_avg",
  unit = "U-Turn: Turn Speed Average",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Turns)

Floodlight Open test code: "five_u_turn"

```{r sens2 five_u_turn turns}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turns",
  unit = "U-Turn: Number of Turns",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Static Balance)

Floodlight Open test code: "static_balance"

```{r sens2 static_balance}
params = list(
  test_code = "static_balance",
  test_metric_code = "sway_path",
  unit = "Static Balance: Sway Path",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Passive Monitoring)

Floodlight Open test code: "mobility"

```{r sens2 mobility}
params = list(
  test_code = "mobility",
  test_metric_code = "life_space_daily",
  unit = "Passive Monitoring: Life Space Daily",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mood (Daily question)

Floodlight Open test code: "daily_questions"

```{r sens2 daily_questions}
params = list(
  test_code = "daily_questions",
  test_metric_code = "mood_response",
  unit = "Daily Question: Mood",
  unit_n = "patient",
  unit_time = "repetition",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

# Sensitivity analysis 3

Performance as a function of weeks since first test
Minimum number of repetitions: 10, minimum number of weeks between first and last: 10

## Cognition (e-SDMT)

Floodlight Open test code: "ips" (information processing speed)

```{r sens3 ips}
params = list(
  test_code = "ips",
  test_metric_code = "correct_responses",
  unit = "e-SDMT: Correct Responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Cognition (e-SDMT corrected)

e-SDMT corrected for dexterity by taking the quotient of correct responses of e-SDMT / Digit Tapping (or in Floodlight's terms: ips / ips_baseline)

```{r sens3 ips_over_ips_baseline}
params = list(
  test_code = "ips_over_ips_baseline",
  test_metric_code = "correct_responses",
  unit = "e-SDMT corrected: Correct Responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Digit Tapping)

Floodlight Open test code: "ips_baseline" (information processing speed baseline)

```{r sens3 ips_baseline}
params = list(
  test_code = "ips_baseline",
  test_metric_code = "correct_responses",
  unit = "Digit Tapping: Correct responses",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Finger Pinching)

Floodlight Open test code: "pinching"

```{r sens3 pinching}
params = list(
  test_code = "pinching",
  test_metric_code = "successful_pinches",
  unit = "Pinching: Successful Pinches",
  unit_n = "hand",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Dexterity (Draw A Shape)

Floodlight Open test code: "draw_a_shape"

```{r sens3 draw_a_shape}
params = list(
  test_code = "draw_a_shape",
  test_metric_code = "number_shapes_drawn_correctly",
  unit = "Drawing: Shapes Drawn Correctly",
  unit_n = "hand",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Two Minute Walk)

Floodlight Open test code: "two_min_walk"

```{r sens3 two_min_walk}
params = list(
  test_code = "two_min_walk",
  test_metric_code = "steps",
  unit = "Two Minute Walk: Steps",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Speed)

Floodlight Open test code: "five_u_turn"

```{r sens3 five_u_turn speed}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turn_speed_avg",
  unit = "U-Turn: Turn Speed Average",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (U-Turn / Turns)

Floodlight Open test code: "five_u_turn"

```{r sens3 five_u_turn turns}
params = list(
  test_code = "five_u_turn",
  test_metric_code = "turns",
  unit = "U-Turn: Number of Turns",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Static Balance)

Floodlight Open test code: "static_balance"

```{r sens3 static_balance}
params = list(
  test_code = "static_balance",
  test_metric_code = "sway_path",
  unit = "Static Balance: Sway Path",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mobility (Passive Monitoring)

Floodlight Open test code: "mobility"

```{r sens3 mobility}
params = list(
  test_code = "mobility",
  test_metric_code = "life_space_daily",
  unit = "Passive Monitoring: Life Space Daily",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

## Mood (Daily question)

Floodlight Open test code: "daily_questions"

```{r sens3 daily_questions}
params = list(
  test_code = "daily_questions",
  test_metric_code = "mood_response",
  unit = "Daily Question: Mood",
  unit_n = "patient",
  unit_time = "week",
  min_repetitions = 10,
  min_weeks = 10,
  up_to_date = "2021-08-01"
)
```
```{r child='single-test-analysis.Rmd', cache=T}
```

